### 2024-02-14 docs/exec-summary/report.qmd
Rephrase the abstract to improve readability

**Results:**
Antidepressants (ATC `N06A`, $c_e$ = `r N06A$ce`, $n_c$ = `r N06A$nc`), antipsychotics (`N05A`, $c_e$ = `r N05A$ce`, $n_c$ = `r N05A$nc`), and anxiolytics (`N05B`, $c_e$ = `r N05B$ce`, $n_c$ = `r N05B$nc`) are psychopharmaca with high eigenvector centrality. These classes of medication are likely to be co-prescribed alongside other medications. Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$ = `r A0x$ce`, $n_c$ = `r A0x$nc`), blood (`B01-B06`, $c_e$ = `r B0x$ce`, $n_c$ = `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$ = `r C0x$ce`, $n_c$ = `r C0x$ne`), analgesics (`N02`, $c_e$ = `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$ = `r R0x$ce`, $n_c$ = `r R0x$nc`). High eigenvector centrality implies that these medications are likely to be co-prescribed with other medications. Only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.

>>>>

**Results:**
Antidepressants (ATC `N06A`, $c_e$ = `r N06A$ce`, $n_c$ = `r N06A$nc`), antipsychotics (`N05A`, $c_e$ = `r N05A$ce`, $n_c$ = `r N05A$nc`), and anxiolytics (`N05B`, $c_e$ = `r N05B$ce`, $n_c$ = `r N05B$nc`) are psychopharmaca with high eigenvector centrality. These classes of medication are likely to be co-prescribed alongside other medications. Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$ = `r A0x$ce`, $n_c$ = `r A0x$nc`), blood (`B01-B06`, $c_e$ = `r B0x$ce`, $n_c$ = `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$ = `r C0x$ce`, $n_c$ = `r C0x$ne`), analgesics (`N02`, $c_e$ = `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$ = `r R0x$ce`, $n_c$ = `r R0x$nc`). Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.
